### 2024-06-27 basic-statistics.qmd
20240627 - sessionInfo() for reproducibility
20240627 - sessionInfo()
20240627 - cross-references

Knowing any three of the following, you can calculate the fourth: statistical power, effect size, sample size, and alpha level.
Below is `R` code for calculating power for each of various statistical tests (i.e., a *power analysis*).
For free point-and-click software for calculating statistical power, see G\*Power: <https://www.psychologie.hhu.de/arbeitsgruppen/allgemeine-psychologie-und-arbeitspsychologie/gpower.html>

@@

Solving for statistical power achieved (given effect size, sample size, and alpha):

@@

Solving for sample size needed (given effect size, power, and alpha):

@@

Solving for minimum effect size needed to detect (given sample size, power, and alpha):

@@

Solving for statistical power achieved (given effect size, sample size per group, and alpha):

@@

Solving for sample size per group needed (given effect size, power, and alpha):

@@

Solving for minimum effect size needed to detect (given sample size per group, power, and alpha):

@@

Solving for sample size needed (given effect size, power, and alpha)—$v = N - \text{numberOfPredictors} - 1$; thus, $N = v + \text{numberOfPredictors} + 1$:

@@

Power analysis for multilevel modeling approaches is more complicated than it is for other statistical analyses, such as correlation, multiple regression, *t*-tests, ANOVA, etc.

@@

Power analysis for latent variable modeling approaches like SEM is more complicated than it is for other statistical analyses, such as correlation, multiple regression, *t*-tests, ANOVA, etc.

@@

There are free tools for calculating power for tests of mediation and moderation:

@@

>>>>

Knowing any three of the following, you can calculate the fourth: statistical power, [effect size](#sec-practicalSignificance), sample size, and [alpha level](#sec-statisticalSignificance).
Below is `R` code for calculating power for each of various statistical tests (i.e., a *power analysis*).
For free point-and-click software for calculating statistical power, see G\*Power: <https://www.psychologie.hhu.de/arbeitsgruppen/allgemeine-psychologie-und-arbeitspsychologie/gpower.html>

@@

Solving for statistical power achieved (given [effect size](#sec-practicalSignificance), sample size, and [alpha level](#sec-statisticalSignificance)):

@@

Solving for sample size needed (given [effect size](#sec-practicalSignificance), power, and [alpha level](#sec-statisticalSignificance)):

@@

Solving for the minimum detectable [effect size](#sec-practicalSignificance) (given sample size, power, and [alpha level](#sec-statisticalSignificance)):

@@

Solving for statistical power achieved (given [effect size](#sec-practicalSignificance), sample size per group, and [alpha level](#sec-statisticalSignificance)):

@@

Solving for sample size per group needed (given [effect size](#sec-practicalSignificance), power, and [alpha level](#sec-statisticalSignificance)):

@@

Solving for the minimum detectable [effect size](#sec-practicalSignificance) (given sample size per group, power, and [alpha level](#sec-statisticalSignificance)):

@@

Solving for sample size needed (given [effect size](#sec-practicalSignificance), power, and [alpha level](#sec-statisticalSignificance))—$v = N - \text{numberOfPredictors} - 1$; thus, $N = v + \text{numberOfPredictors} + 1$:

@@

Power analysis for multilevel modeling approaches is more complicated than it is for other statistical analyses, such as [correlation](#sec-correlation), [multiple regression](#multipleRegression), [*t*-tests](#sec-tTest), [ANOVA](@sec-anova), etc.

@@

Power analysis for latent variable modeling approaches like structural equation modeling (SEM) is more complicated than it is for other statistical analyses, such as [correlation](#sec-correlation), [multiple regression](#multipleRegression), [*t*-tests](#sec-tTest), [ANOVA](@sec-anova), etc.

@@

There are free tools for calculating power for tests of [mediation](#mediation) and [moderation](#moderation):

@@

::: {.content-visible when-format="html"}

## Session Info {#sec-basicStatsSessionInfo}

```{r}
sessionInfo()
```

:::
